A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-06-08 report_clean_merged/FD.tex
added report merged with the files of Lise-Marie and Bruno

\section{Frequency domain study}
The goal of this section is to review the connection between the frequency domain counterpart of the problem (\ref{eq:main_model}) and 
the regularized problem (\ref{eq:seq_regularized}).

The model (\ref{eq:main_model}) can be rewritten in the frequency domain as 
\bealn
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\uuline{\varepsilon_{\omega}^{\nu}}(x)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,\\
\uuline{\varepsilon_{\omega}^{\nu}}(x)=\left(
\begin{matrix}
 \alpha^{\nu}_{\omega}(x) & -i\delta^{\nu}_{\omega}(x) \\
 i\delta^{\nu}_{\omega}(x) & \alpha^{\nu}_{\omega}(x)
\end{matrix}
\right),\qquad 
 \alpha^{\nu}_{\omega}(x)=1-\frac{\omega_{\nu}\omega_p^2(x)}{\omega(\omega_{\nu}^2-\omega_c^2(x))},\qquad 
\delta^{\nu}_{\omega}(x)=\frac{\omega_c(\mathbf{r})\omega_p^2(x)}{\omega(\omega_{\nu}^2-\omega_c^2(x))},
\eealn
where the frequency 
$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. \arev{Notice that neither cyclotron, nor hybrid resonances occur in the problem 
with the dielectric tensor $\uuline{\varepsilon_{\omega}^{\nu}}(x), \; \nu>0$ (since all the problem parameters are real). Hence 
the choice of the non-zero plasma friction $\nu>0$ can be viewed as a regularization of the problem. }

\mrev{
The series expansion as $\nu\rightarrow 0$ gives at leading orders
\bealn
 \alpha^{\nu}_{\omega}=\alpha_{\omega}+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{\omega(\omega^2-\omega_c^2)^2}=\alpha_{\omega}+i\nu D_{\alpha},\\
 \delta^{\nu}_{\omega}=\delta_{\omega}-i\nu\frac{2\omega_c\omega_p^2}{(\omega^2-\omega_c^2)^2}=\delta_{\omega}+i\nu D_{\delta},
\eealn
where $\alpha_{\omega},\;\delta_{\omega}$ are defined by (\ref{eq:alpha_delta}). In the frequency domain one thus can consider 
the following regularization of the cold plasma dielectric tensor of the above problem, valid as $\nu\rightarrow 0$:
\begin{align*}
\uuline{\varepsilon_{\omega}^{\nu}}\approx \uuline{\varepsilon_{\omega}^{0}}+i\nu \left(
 \begin{matrix}
  D_{\alpha} & -D_{\delta}\\
  D_{\delta} & D_{\alpha}
 \end{matrix}
\right).
\end{align*}
However, as demonstrated in \cite{singular_solutions} for the 1D setting, a significantly simpler regularization (considered in \cite{Despres_2014})
\ben
\uuline{\varepsilon_{\omega}^{\nu}}(x)\approx \uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}
\een
yields the same solution as $\nu\rightarrow 0$. }
Thus, applying the above process to (\ref{eq:main_model}) in the frequency domain, we obtain, see also \cite{Despres_2014},
\begin{align*}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\left(\uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}\right)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,\\
\uuline{\varepsilon_{\omega}^{0}}(x)=\left(
\begin{matrix}
 \alpha_{\omega}(x) & -i\delta_{\omega}(x) \\
 i\delta_{\omega}(x) & \alpha_{\omega}(x)
\end{matrix}
\right). 
\end{align*}
\mrev{
For brevity, from now on we will denote $\frac{\omega^2}{c^2}\alpha_{\omega},\; \frac{\omega^2}{c^2}\delta_{\omega}$ by $\alpha,\; \delta$ and consider a sequence of regularized problems. 
\begin{align}
\label{eq:main_frequency_domain}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-
\left(\uuline{\varepsilon}^{0}(x)+i\nu \mathrm{Id}\right)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,\\
\label{eq:epsilon_0}
\uuline{\varepsilon}^{0}(x)=\left(
\begin{matrix}
 \alpha(x) & -i\delta(x) \\
 i\delta(x) & \alpha(x)
\end{matrix}
\right),
\end{align}
where $\alpha,\;\delta$ satisfy the following assumption.
}
\urev{
\begin{assumption}
\label{assumption:smooth}
The coefficients  $\alpha(x)$ and $\delta(x)$ are assumed to be sufficiently smooth, i.e. bounded and continuous in  
$\left[-L,\; H\right]$.
\end{assumption}
This assumption can be ensured, for example, by requiring the continuity of $N_e(x), B_0(x)$ in $[-L,\;H]$ and the absence of the cyclotron resonance, i.e. for all $x$ $|\omega_c^2(x)-\omega^2(x)|>c>0$ on this interval. 
}
\urev{
\begin{remark}
For the time domain problem (\ref{eq:main_model}) the choice of the sign of $\nu>0$ is of crucial importance for the stability of the problem. 
In the frequency domain, as we can see from the above and from \cite{Despres_2014,LMIG_thesis}, the sign 
of the parameter $\nu$ can be chosen arbitrarily to regularize the problem. 
However, as demonstrated in the aforementioned works, as $\nu\rightarrow 0\pm$, the 
corresponding limiting solutions differ, though both exhibit the singularity in the point of the hybrid resonance.  
\end{remark}
}
%%%%%%%%%%%%%%%%%%%%%% 
\mrev{\subsection{Well-Posedness of the Frequency Domain Problem}}
%%%%%%%%%%%%%%%%%%%%%% 
\label{sec:wellposedness}

%In order to reduce problem \eqref{eq:main_frequency_domain} to one dimension, perform a Fourier transform in the $y$ variable, 
%denoting by $\theta$ the corresponding Fourier variable. 
\mrev{In this section we study the well-posedness of the problem (\ref{eq:main_frequency_domain}) with the 
 boundary conditions (\ref{eq:boundary_conditions_intro}) with the help of Lax-Milgram lemma.} 
After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space of the problem  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$, 
equipped with the norm
\ben
 \|\mathbf{v}\|_{\mathbf{V}}^2= \|v_1\|_{L^{2}(\Omega)}^2+\|v_2\|_{H^{1}(\Omega)}^2,
\een
the resulting one-dimensional system can be rewritten in the following variational form:
\begin{align}
\label{vf1dcase}
\begin{array}{l}
\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\tilde E_y' -\urev{i} \theta \tilde E_x)} - \int_{-L}^H (\uuline{\varepsilon}^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\tilde \E}
%\\ \displaystyle 
 - i \lambda E_y (-L)\overline{ \tilde E_y (-L)} = -g_{inc} (-L) \overline{( \tilde E_y(-L) )},
\end{array}\\
\nonumber
\text{ for all } \tilde{\mathbf{E}}=(\tilde E_x,\tilde E_y)\in \mathbf{V}.
\end{align}
Recall that here $\lambda\geq 0$. 
%=\omega\geq 0$. 
Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\hat{E}_{x,y}$ for convenience. \mrev{Also, 
by $\|u\|_{L^{2}}$ we will denote $\|u\|_{L^{2}(\Omega)}$, for $u\in L^2(\Omega)$, and $\|\ubf\|_{L^2(\Omega)}=\left(\|u_1\|^2_{L^2}+\|u_2\|^2_{L^2}\right)^{\frac{1}{2}}$, 
for $\ubf=(u_1,\;u_2)\in \left(L^2(\Omega)\right)^2$.}

The above can be reformulated as, \urev{for the unknown $\mathbf{E}$ and $\tilde{\mathbf{E}}$ a test function},
\ben
a\left(\mathbf{E},\tilde{\mathbf{E}}\right)=l(\tilde{\mathbf{E}}), \; \text{ for all }\tilde{\mathbf{E}}\in \mathbf{V},
\een
with a bilinear form $a$ and a linear form $l$, \urev{defined for $\mathbf{u},\; \mathbf{v}\in \mathbf{V}$}:
\ben
a(\ubf,\vbf) = a_1 (\ubf,\vbf) +i a_2(\ubf,\vbf)\  \text{ and } \  l(\vbf) = -g_{inc} (-L) \overline{(v_2(-L) )} 
\een
where $a_1= a_1^*$ and $a_2=a_2^*$ are hermitian
\ben
\left\{\begin{array}{l}
	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \uuline{\varepsilon}^{0} \ubf\cdot \overline{\vbf}, 
	\\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} - \lambda u_2 (-L) \overline{v_2 (-L)} , 
\end{array}\right.
\een

\urev{
Let us denote the spectral radius of $\uuline{\varepsilon}^{0}$ by $\heps =  \|\rho(\uuline{\varepsilon}^{0})\|_{L^{\infty}(\Omega)}$. 
By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta^2\|_{L^{\infty}(\Omega)}, \|\alpha-\delta^2\|_{L^{\infty}(\Omega)}\right)$ 
is bounded.}
%\end{df}

@@

\begin{lemma}
\label{lemma:well_posedness}
\urev{Let Assumption \ref{assumption:smooth} hold}. Then the bilinear form 
\ben
 a(\ubf,\vbf):  \mathbf{V}\times \mathbf{V}\rightarrow \mathbb{C}
\een
is continuous and coercive for all \mrev{$\lambda\geq 0$} and $\nu>0$: for all $\ubf,\vbf\in \mathbf{V}$ it holds that
\bealn
\label{eq:bilinear_cont}
\left\{\begin{array}{l}
\Re\left(\mathrm{e}^{i\urev{\beta_{\nu}}}a(\ubf,\ubf)\right)\geq \frac{|\nu|}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right),\; 
\text{ for some $\urev{\beta_{\nu}}\in\left(0,\frac{\pi}{2}\right)$},\\
|a(\ubf,\vbf)|\leq C \|\ubf\|_{\mathbf{V}}\|\vbf\|_{\mathbf{V}},
\end{array}\right.
\eealn
where $C>0$ does not depend on $\nu$. The problem~\eqref{vf1dcase} is well-posed in $\mathbf{V}$.

\end{lemma}
\begin{proof}
	The boundedness of $a$ is obvious using the continuous embedding in dimension
	one  $H^1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
	\mrev{Given $\heps$ the spectral radius of $\uuline{\varepsilon}^{0}$, 
	$\heps \mathrm{Id}- \uuline{\varepsilon}^{0} $ is a non-negative hermitian matrix.}
	Therefore
	\ben
	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps \mathrm{Id} - \uuline{\varepsilon}^{0} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
	\geq \frac12 \|u_2 '  \|_{L^2}^ 2 -
	\theta ^2 \| u_1 \|_{L^2}^ 2.
	\een
	Thus one can write
	$
	a_1(\ubf,\ubf)  \geq \frac{1}{2}\|u_2'\|^2_{L^2}-  (\heps  +  \theta^2) \| \ubf \|_{L^2}^2$.
	One also has that, \mrev{for $\lambda \geq 0$},
	$
	a_2 (\ubf ,\ubf) \leq -\nu \| \ubf \|_{L^2}^2$. 
	Therefore
	\ben
	a_1(\ubf,\ubf)-\frac{\heps  +  \theta^2 + 1 }\nu a_2(\ubf,\ubf)\geq \frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2,
	\een
	or, introducing $\beta_{\nu}=\arccos\frac{1}{\sqrt{1+\left(\heps+\theta^2+1\right)^2\nu^{-2}}}$, this is equivalent to 
	\ben
	\Re\left(\mathrm{e}^{i\beta_{\nu}}a(\ubf,\ubf)\right)\geq 
	\frac{1}{\sqrt{1+\left(\heps+\theta^2+1\right)^2\nu^{-2}}} \left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right)\\
	\geq \frac{\nu}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right).
	\een	
	The problem \eqref{vf1dcase} is uniquely solvable thanks to Lax-Milgram theorem.
\end{proof}
\begin{remark}
\mrev{Note that in the case $\lambda=0$, one can show that the problem is well-posed for all $\nu\neq 0$, since $a_2(\ubf,\ubf)=-\nu\|\ubf\|_{L^2}^2$ and 
thus in the above proof
\begin{align*}
a_1(\ubf,\ubf)-\frac{\heps  +  \theta^2 + 1 }\nu a_2(\ubf,\ubf)=\left(a_1(\ubf,\ubf)+(\heps  +  \theta^2)\|\ubf\|_{L^2}^2\right)+\|\ubf\|_{L^2}^2.
\end{align*}
Similarly, in the case $\lambda<0$, it is possible to demonstrate the well-posedness of the problem for $\nu<0$. 
}
\end{remark}
\begin{remark} 
\label{remark:other}
The above proof is not optimal in the case when $\left|\alpha(x)\right|>c>0$ for $c>0$ on the whole interval $[-L,\; H]$, at least 
for the case $\theta=0$. In this case the problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. More precisely, it can be written 
as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$ \mrev{and the boundary conditions (\ref{eq:boundary_conditions_frequency_domain})}, and the second equation 
\begin{align*}
  \left(E_x,u\right)=\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
\end{align*}
uniquely defines $E_x\in L^{2}(\Omega)$. The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, we can obtain $E_x$ from the second equation.
\end{remark}

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Discretization of the Frequency Domain Problem}
\label{sec:discr}
Testing the variational formulation (\ref{vf1dcase}) with $(\tilde E_x,0)$ and $(0,\; \tilde{E}_y)\in\mathbf{V}$ and using 
an explicit expression for the tensor of the dielectric permittivity (\ref{eq:epsilon_0}), we can rewrite it as a system of two equations
%\begin{align*}
%\begin{split}
%i\theta \displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{\tilde E_x} - \int_{-L}^H \left((\epsilon_0 +i\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{x}
%&=0,\\
%\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\tilde {E_y'} - \int_{-L}^H\left( (\epsilon_0 +i\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{y}
%  - i \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
%  \text{ for all } \tilde E_x\in L^{2}(\Omega), \; \tilde{E}_{y}\in H^{1}(\Omega).
%  \end{split}
%\end{align*}
%Using the explicit expression for the dielectric permittivity tensor in the above, it yields:

>>>>

\section{Frequency domain study}
This section reviews the connection between the frequency domain counterpart of the problem (\ref{eq:main_model}) and 
the regularized problem (\ref{eq:seq_regularized}).

Model (\ref{eq:main_model}) can be rewritten in the frequency domain as 
\bealn
\left(
\begin{matrix}
 i\theta \partial_x \widehat{E}_y+\theta^2 \widehat{E}_x\\
 i\theta \partial_x \widehat{E}_x -\partial_x^2 \widehat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\uuline{\varepsilon_{\omega}^{\nu}}(x)\left(
\begin{matrix}
 \widehat{E}_x\\
 \widehat{E}_y
\end{matrix}
\right)
=0,\\
\uuline{\varepsilon_{\omega}^{\nu}}(x)=\left(
\begin{matrix}
 \alpha^{\nu}_{\omega}(x) & -i\delta^{\nu}_{\omega}(x) \\
 i\delta^{\nu}_{\omega}(x) & \alpha^{\nu}_{\omega}(x)
\end{matrix}
\right),\qquad 
 \alpha^{\nu}_{\omega}(x)=1-\frac{\omega_{\nu}\omega_p^2(x)}{\omega(\omega_{\nu}^2-\omega_c^2(x))},\qquad 
\delta^{\nu}_{\omega}(x)=\frac{\omega_c(\mathbf{r})\omega_p^2(x)}{\omega(\omega_{\nu}^2-\omega_c^2(x))},
\eealn
where the frequency 
$\omega_{\nu}=\omega+i\nu$ is shifted in the complex plane. \arev{ %Notice that neither cyclotron, nor hybrid resonances occur in the problem 
%with the dielectric tensor $\uuline{\varepsilon_{\omega}^{\nu}}(x), \; \nu>0$ (since all the problem parameters are real). Hence 
%t
The choice of the non-zero plasma friction $\nu>0$ is a regularization of the problem. }

\mrev{
A series expansion as $\nu\rightarrow 0$ gives at leading orders
\bealn
 \alpha^{\nu}_{\omega}=\alpha_{\omega}+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{\omega(\omega^2-\omega_c^2)^2}=\alpha_{\omega}+i\nu D_{\alpha},\\
 \delta^{\nu}_{\omega}=\delta_{\omega}-i\nu\frac{2\omega_c\omega_p^2}{(\omega^2-\omega_c^2)^2}=\delta_{\omega}+i\nu D_{\delta},
\eealn
where $\alpha_{\omega},\;\delta_{\omega}$ are defined by (\ref{eq:alpha_delta}). %In the frequency domain 
One thus can consider 
the following regularization of the cold plasma dielectric tensor of the above problem, valid as $\nu\rightarrow 0$:
\begin{align*}
\uuline{\varepsilon_{\omega}^{\nu}}\approx \uuline{\varepsilon_{\omega}^{0}}+i\nu \left(
 \begin{matrix}
  D_{\alpha} & -D_{\delta}\\
  D_{\delta} & D_{\alpha}
 \end{matrix}
\right).
\end{align*}
However, as demonstrated in \cite{singular_solutions} for the 1D setting, a significantly simpler regularization (considered in \cite{Despres_2014})
\ben
\uuline{\varepsilon_{\omega}^{\nu}}(x)\approx \uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}
\een
yields to the same limit solution as $\nu\rightarrow 0$. }
As a consequence we will consider in this work the simpler regularized system
%Thus, applying the above process to (\ref{eq:main_model}) in the frequency domain, we obtain, see also \cite{Despres_2014},
\begin{align*}
\left(
\begin{matrix}
 i\theta \partial_x \widehat{E}_y+\theta^2 \widehat{E}_x\\
 i\theta \partial_x \widehat{E}_x -\partial_x^2 \widehat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\left(\uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}\right)\left(
\begin{matrix}
 \widehat{E}_x\\
 \widehat{E}_y
\end{matrix}
\right)
=0,\\
\uuline{\varepsilon_{\omega}^{0}}(x)=\left(
\begin{matrix}
 \alpha_{\omega}(x) & -i\delta_{\omega}(x) \\
 i\delta_{\omega}(x) & \alpha_{\omega}(x)
\end{matrix}
\right). 
\end{align*}
\mrev{
For brevity, from now on we will denote $\frac{\omega^2}{c^2}\alpha_{\omega},\; \frac{\omega^2}{c^2}\delta_{\omega}$ by $\alpha,\; \delta$ and consider a sequence of regularized problems. 
\begin{align}
\label{eq:main_frequency_domain}
\left(
\begin{matrix}
 i\theta \partial_x \widehat{E}_y+\theta^2 \widehat{E}_x\\
 i\theta \partial_x \widehat{E}_x -\partial_x^2 \widehat{E}_y
\end{matrix}
\right)-
\left(\uuline{\varepsilon}^{0}(x)+i\nu \mathrm{Id}\right)\left(
\begin{matrix}
 \widehat{E}_x\\
 \widehat{E}_y
\end{matrix}
\right)
=0,\\
\label{eq:epsilon_0}
\uuline{\varepsilon}^{0}(x)=\left(
\begin{matrix}
 \alpha(x) & -i\delta(x) \\
 i\delta(x) & \alpha(x)
\end{matrix}
\right),
\end{align}
where $\alpha,\;\delta$ satisfy the following assumption.
}
\urev{
\begin{assumption}
\label{assumption:smooth}
The coefficients  $\alpha(x)$ and $\delta(x)$ are assumed to be sufficiently smooth, i.e. continuous in  
$\left[-L,\; H\right]$.
\end{assumption}
This assumption can be ensured, for example, by requiring the continuity of $N_e(x), B_0(x)$ in $[-L,\;H]$ and the absence of the cyclotron resonance, i.e. for all $x$ $|\omega_c^2(x)-\omega^2(x)|>c>0$ on this interval. 
}
\urev{
\begin{remark}
For the time domain problem (\ref{eq:main_model}) the choice of the sign of $\nu>0$ is of crucial importance for the stability of the problem. 
In the frequency domain, as we can see from the above and from \cite{Despres_2014,LMIG_thesis}, the sign 
of the parameter $\nu$ can be chosen arbitrarily to regularize the problem. 
However, as demonstrated in the aforementioned works, as $\nu\rightarrow 0\pm$, the 
corresponding limiting solutions differ, though both exhibit the singularity in the point of the hybrid resonance.  
\end{remark}
}
%%%%%%%%%%%%%%%%%%%%%% 
\mrev{\subsection{Well-Posedness of the Frequency Domain Problem}}
%%%%%%%%%%%%%%%%%%%%%% 
\label{sec:wellposedness}

%In order to reduce problem \eqref{eq:main_frequency_domain} to one dimension, perform a Fourier transform in the $y$ variable, 
%denoting by $\theta$ the corresponding Fourier variable. 
\mrev{In this section we study the well-posedness of Problem (\ref{eq:main_frequency_domain}) with the 
 boundary conditions (\ref{eq:boundary_conditions_intro}), thanks to the Lax-Milgram lemma.} 
After introducing $\Omega=(-L,\; H)\subset \mathbb R$ and defining the function space  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$, 
equipped with the norm
\ben
 \|\mathbf{v}\|_{\mathbf{V}}^2= \|v_1\|_{L^{2}(\Omega)}^2+\|v_2\|_{H^{1}(\Omega)}^2,
\een
the resulting one-dimensional system reads in the following variational form:
\begin{align}
\label{vf1dcase}
\begin{array}{l}
\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{(\widetilde E_y' -\urev{i} \theta \widetilde E_x)} 
- \int_{-L}^H (\uuline{\varepsilon}^{0} +i\nu \mathrm{Id}) \E \cdot \overline{\widetilde \E}
%\\ \displaystyle 
 - i \lambda E_y (-L)\overline{ \widetilde E_y (-L)} = -g_{inc} (-L) \overline{( \widetilde E_y(-L) )},
\end{array}\\
\nonumber
\text{ for all } \widetilde{\mathbf{E}}=(\widetilde E_x,\widetilde E_y)\in \mathbf{V}.
\end{align}
Recall that here $\lambda\geq 0$. 
%=\omega\geq 0$. 
Let us remark that in this and further sections, where it is not ambiguous, we will use the notation $E_{x,y}$ instead of $\widehat{E}_{x,y}$ for convenience. \mrev{Also, 
by $\|u\|_{L^{2}}$ we will denote $\|u\|_{L^{2}(\Omega)}$, for $u\in L^2(\Omega)$, and $\|\ubf\|_{L^2(\Omega)}=\left(\|u_1\|^2_{L^2}+\|u_2\|^2_{L^2}\right)^{\frac{1}{2}}$, 
for $\ubf=(u_1,\;u_2)\in \left(L^2(\Omega)\right)^2$.}

For the sake of conciseness, consider the following definitions. Let $a$ and $l$ be the bilinear and linear forms, \urev{defined for $\mathbf{u},\; \mathbf{v}\in \mathbf{V}$}:
\ben
a(\ubf,\vbf) = a_1 (\ubf,\vbf) +i a_2(\ubf,\vbf)\  \text{ and } \  l(\vbf) = -g_{inc} (-L) \overline{(v_2(-L) )} 
\een
where $a_1= a_1^*$ and $a_2=a_2^*$ are hermitian
\ben
\left\{\begin{array}{l}
	a_1(\ubf,\vbf) = \int_{-L}^H (u_2' -i\theta u_1)\overline{(v_2' -i \theta v_1)} - \int_{-L}^H \uuline{\varepsilon}^{0} \ubf\cdot \overline{\vbf}, 
	\\ a_2(\ubf,\vbf) = -\nu \int_{-L}^H  \ubf\cdot \overline{\vbf} - \lambda u_2 (-L) \overline{v_2 (-L)}.
\end{array}\right.
\een
Then \eqref{vf1dcase} reads: \urev{find $\mathbf{E}$ such that},
\ben
a\left(\mathbf{E},\tilde{\mathbf{E}}\right)=l(\tilde{\mathbf{E}}), \; \text{ for all }\tilde{\mathbf{E}}\in \mathbf{V}.
\een

\urev{
Let us denote the spectral radius of $\uuline{\varepsilon}^{0}$ by $\heps =  \|\rho(\uuline{\varepsilon}^{0})\|_{L^{\infty}(\Omega)}$. 
By Assumption \ref{assumption:smooth}, the spectral radius $\heps=\max\left(\|\alpha+\delta\|_{L^{\infty}(\Omega)}, \|\alpha-\delta\|_{L^{\infty}(\Omega)}\right)$ 
is bounded.}
%\end{df}

@@

\begin{lemma}
\label{lemma:well_posedness}
\urev{Let Assumption \ref{assumption:smooth} hold}. Then the bilinear form 
\ben
 a(\ubf,\vbf):  \mathbf{V}\times \mathbf{V}\rightarrow \mathbb{C}
\een
is continuous and coercive for all \mrev{$\lambda\geq 0$} and $\nu>0$: for all $\ubf,\vbf\in \mathbf{V}$ it holds that
\bealn
\label{eq:bilinear_cont}
\left\{\begin{array}{l}
\Re\left(\mathrm{e}^{i\urev{\beta_{\nu}}}a(\ubf,\ubf)\right)\geq \frac{|\nu|}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right),\; 
\text{ for some $\urev{\beta_{\nu}}\in\left(0,\frac{\pi}{2}\right)$},\\
|a(\ubf,\vbf)|\leq C \|\ubf\|_{\mathbf{V}}\|\vbf\|_{\mathbf{V}},
\end{array}\right.
\eealn
where $C>0$ does not depend on $\nu$. Problem~\eqref{vf1dcase} is well-posed in $\mathbf{V}$.

\end{lemma}
\begin{proof}
	The boundedness of $a$ is obvious using the continuous embedding in dimension
	one  $H^1(\Omega)\subset C^0(\overline \Omega)$. Let us focus on the proof of coercivity. 
	\mrev{Given $\heps$ the spectral radius of $\uuline{\varepsilon}^{0}$, 
	$\heps \mathrm{Id}- \uuline{\varepsilon}^{0} $ is a non-negative hermitian matrix.}
	Therefore
	\ben
	a_1(\ubf,\ubf) + \heps\|\ubf\|^2_{L^2}= \|u_2' - i \theta u_1 \|^2_{L^2} + \left( (\heps \mathrm{Id} - \uuline{\varepsilon}^{0} ) \ubf, \overline{\ubf} \right)  \geq \|u_2 ' - i \theta u_1 \|_{L^ 2}^ 2
	\geq \frac12 \|u_2 '  \|_{L^2}^ 2 -
	\theta ^2 \| u_1 \|_{L^2}^ 2.
	\een
	Thus
	$
	a_1(\ubf,\ubf)  \geq \frac{1}{2}\|u_2'\|^2_{L^2}-  (\heps  +  \theta^2) \| \ubf \|_{L^2}^2$.
	On the other hand, \mrev{for $\lambda \geq 0$},
	$
	a_2 (\ubf ,\ubf) \leq -\nu \| \ubf \|_{L^2}^2$. 
	Therefore
	\ben
	a_1(\ubf,\ubf)-\frac{\heps  +  \theta^2 + 1 }\nu a_2(\ubf,\ubf)\geq \frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2,
	\een
	or, introducing $\beta_{\nu}=\arccos\frac{1}{\sqrt{1+\left(\heps+\theta^2+1\right)^2\nu^{-2}}}$, this is equivalent to 
	\ben
	\Re\left(\mathrm{e}^{i\beta_{\nu}}a(\ubf,\ubf)\right)\geq 
	\frac{1}{\sqrt{1+\left(\heps+\theta^2+1\right)^2\nu^{-2}}} \left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right)\\
	\geq \frac{\nu}{\sqrt{(\heps+\theta^2+1)^2+\nu^2}}\left(\frac{1}{2}\|u_2'\|^2_{L^2}  + \| \ubf \|_{L^2}^2\right).
	\een	
	Problem \eqref{vf1dcase} is then uniquely solvable thanks to Lax-Milgram theorem.
\end{proof}
%
%
%\begin{remark}
%\mrev{Not the variational problem can be proved well-posed
%with the same method for  slightly different coefficients.
%%For example for $\lambda<0$ and  Note that in the case $\lambda=0$, one can show that the problem is well-posed for all $\nu< 0$, since $a_2(\ubf,\ubf)=-\nu\|\ubf\|_{L^2}^2$ and 
%%thus in the above proof
%%\begin{align*}
%%a_1(\ubf,\ubf)-\frac{\heps  +  \theta^2 + 1 }\nu a_2(\ubf,\ubf)=\left(a_1(\ubf,\ubf)+(\heps  +  \theta^2)\|\ubf\|_{L^2}^2\right)+\|\ubf\|_{L^2}^2.
%%\end{align*}
%%Similarly, in the case $\lambda<0$, it is possible to demonstrate the well-posedness of the problem for $\nu<0$. 
%}
%\end{remark}

\begin{remark} 
\label{remark:other}
The above proof is not optimal when the diagonal coefficient is uniformly positive, namely 
$\alpha(x)>c$ for some $c>0$ on the whole interval $[-L,\; H]$, at least 
for the case $\theta=0$. In this particular case Problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. More precisely, it can be written 
as a system of two equations, the first equation (for $E_y$) being the variational formulation for the Helmholtz equation 
with the variable coefficient $k^2=(\alpha-\frac{\delta^2}{\alpha})$ \mrev{coupled to boundary conditions (\ref{eq:boundary_conditions_frequency_domain})}, and the second equation being  
\begin{align*}
  \left(E_x,u\right)=\left(\frac{i\delta}{\alpha}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega).
\end{align*}
The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, $E_x\in L^{2}(\Omega)$ is uniquely defined from the latter equation.
\end{remark}

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Discretization of the Frequency Domain Problem}
\label{sec:discr}
Testing the variational formulation (\ref{vf1dcase}) with $(\tilde E_x,0)$ and $(0,\; \tilde{E}_y)\in\mathbf{V}$ and using 
an explicit expression for the tensor of the dielectric permittivity (\ref{eq:epsilon_0}), we get the following system of two equations
%\begin{align*}
%\begin{split}
%i\theta \displaystyle \int_{-L}^H (E_y' -i\theta E_x)\overline{\tilde E_x} - \int_{-L}^H \left((\epsilon_0 +i\nu \operatorname{Id}) \E\right)_{1} \overline{\tilde E}_{x}
%&=0,\\
%\displaystyle \int_{-L}^H (E_y' -i\theta E_x)\tilde {E_y'} - \int_{-L}^H\left( (\epsilon_0 +i\nu\operatorname{Id}) \E\right)_{2}\overline{\tilde{E}}_{y}
%  - i \lambda E_y (-L) \tilde E_y (-L) &= -g_{inc} (-L) \overline{( \tilde E_y(-L) )},\\
%  \text{ for all } \tilde E_x\in L^{2}(\Omega), \; \tilde{E}_{y}\in H^{1}(\Omega).
%  \end{split}
%\end{align*}
%Using the explicit expression for the dielectric permittivity tensor in the above, it yields:
